---
title: "PANDA Weekly Report"
author: "Shreya Sheth"
date: "June 10, 2021"
output:
  html_document:
    code_folding: hide
    df_print: kable
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
  pdf_document:
    code_folding: hide
    df_print: kable
    number_sections: no
    toc: yes
    toc_depth: 2
---
<style type="text/css">
body{ font-size: 18px; max-width: 1600px; margin: auto; padding: 1em; }
code.r{ font-size: 20px; }
p { padding-top: 8px; padding-bottom: 8px; }
pre { font-size: 16px; }
</style>

```{r setup, include=FALSE, warning = F}
#this is just some basic setup
if (!require(pacman)) { install.packages("pacman"); library(pacman) } #sets up pacman package, which simplifies loading of all the packages below
p_load(knitr, tidyverse, psych, R.matlab, reshape2, ggplot2, cowplot, lme4, flextable, emmeans) #packages to load
knitr::opts_chunk$set(echo = TRUE) #print code by default
options(digits=3) 

panda_protocol=list(name="PANDA",
                        redcap_uri='https://www.ctsiredcap.pitt.edu/redcap/api/',
                        token='CD9DCB5E2B863E04684C111F7A6C22F2',
                        forcenewsubinsync=TRUE)

```

# PANDA Weekly Report and Data Summary

## Overview of Recruitment

```{r, message = FALSE, warning = FALSE}
# First, let's make a table to provide a regular update on recruitment. 
# Work towards doing this programmatically, so that the numbers get pulled from redcap each time the markdown is generated, as opposed to you having to manually update them

#pull record registration form from REDCap
recruitment<-bsrc::bsrc.getform(protocol = panda_protocol,online = TRUE,formname = "record_registration")

#remove IDs that aren't real subjects

recruitment$record_id <- as.numeric(recruitment$record_id)
recruitment_data <- recruitment %>% filter(!is.na(record_id))

#Get recruitment stats
##Completed <- 15 # number of subjects that have completed the protocol

#cat("Completed  = " , sum(!is.na(recruitment_data$panda_checklist___2)))

Completed <- sum(!is.na(recruitment_data$panda_checklist___2))

##Part1_Only <- 4 # number of subjects that have completed part 1 only
#cat("Part1_Only  = " , sum(is.na(recruitment_data$panda_checklist___2)))

Part1_Only <- sum(is.na(recruitment_data$panda_checklist___2))

#Total_Enrolled <- Completed + Part1_Only # number of subjects enrolled in the study (consented)
#cat("Total_Enrolled  = " , sum(!is.na(recruitment_data$panda_consent)))

Total_Enrolled <- sum(!is.na(recruitment_data$panda_consent))

#ss_csv <- read_csv("~/Box/skinner/protocols/PANDA/Scheduling and Tracking/Panda Screening and Scheduling.csv") #need this to be a csv
#filter removes empty rows
#ss_csv <- ss_csv %>% filter(Intials != "") 
#Total_Screened <- nrow(ss_csv) #number of rows will be equal to number of participants screened

Scheduled_NotRun <- 3 # number of subjects that have been scheduled but not yet run - add from excel?
Dropouts <- 2
Ineligible <- 1
Need_to_Screen <- 24 # subjects that need to be screened - add from excel? 
Total_Screened <- 75 # number of subjects that have been screened - should screened include people not in redcap?

#panda_screening=list(name="panda_screening",
                        #redcap_uri='https://www.ctsiredcap.pitt.edu/redcap/api/',
                        #token='83419F4206440B5D26B1FC3B465DB2F7',
                        #forcenewsubinsync=TRUE)

#screening<-bsrc::bsrc.getform(protocol = panda_screening,online = TRUE,formname = "eligibility_screening_phone_or_unit")

#screening_data <- screening %>% filter(egs_whichblrub == "5")

#cat("Total_Screened  = " , sum(!is.na(screening_data$egs_whichblrub)))


Screen2Run_Conversion <- ((Part1_Only+Completed) / Total_Screened)*100 # Screen to Completion Conversion rate

(recruitment_table <- data.frame(Completed, Part1_Only, Dropouts, Ineligible, Total_Enrolled, Scheduled_NotRun, Need_to_Screen, Total_Screened, Screen2Run_Conversion) %>% pivot_longer(Completed:Screen2Run_Conversion, names_to = "Metric", values_to = "Value"))

```

## Demographic and Clinical Characterization of Part 1 Completers

```{r, message = FALSE, warning= FALSE}

# Overall Sample First

demo<-bsrc::bsrc.getform(protocol = panda_protocol,online = TRUE,formname = "demographic_information")

#get rid of character ids
demo$record_id <- as.numeric(demo$record_id)
demo <- demo %>% filter(!is.na(record_id))

#mean age of the sample 
Mean_Age <- mean(demo$demo_age) 
#cat("Mean_Age  = " , mean(demo$demo_age))

#standard deviation of age in the sample 
SD_Age <- sd(demo$demo_age) 
#cat("SD_Age  = " , sd(demo$demo_age))

N_Female <- table(demo$demo_gender)[2]
N_Male <- table(demo$demo_gender)[1]
N_Asian <- sum(demo$demo_race___1, na.rm = T)
N_AmIndianNative <- sum(demo$demo_race___2, na.rm = T)
N_Black <- sum(demo$demo_race___3, na.rm = T)
N_HisLatinx <- sum(demo$demo_race___4, na.rm = T)
N_NatHawPi <- sum(demo$demo_race___5, na.rm = T)
N_White <- sum(demo$demo_race___6, na.rm = T)
N_NoAns <- sum(demo$demo_race___7, na.rm = T)
N_Other <- sum(demo$demo_race___8, na.rm = T)
N_Single <- table(demo$demo_maritalstatus)[1]
MedianIncome18 <- median(demo$demo_income)
MedianEducation18 <- median(demo$demo_education)

#make the table
demographic_table <- data.frame(Mean_Age, SD_Age, N_Female, N_Asian, N_AmIndianNative, N_Black, N_HisLatinx, N_NatHawPi, N_White, N_NoAns, N_Other, N_Single, MedianIncome18, MedianEducation18, row.names = NULL) %>% pivot_longer(Mean_Age:MedianEducation18, names_to = "Demographic", values_to = "Value")

#percentages can be helpful for some of these, so let's add a column for those
(demographic_table <- demographic_table %>% mutate(Percent = if_else(grepl('^N_', demographic_table$Demographic), ((demographic_table$Value / Completed) * 100), NA_real_)))

#for income, let's convert it to a factor, specify levels, and plot: 
demo$demo_income <- as.factor(demo$demo_income)
levels(demo$demo_income) <- c("<25k", "25-35k", "35-50k", "50-75k", "75-100k", "100-150k", ">150k", "No Answer")

ggplot(demo, aes(x = demo_income)) + geom_histogram(stat = "count") + theme_cowplot()

#same deal for education
demo$demo_education <- as.factor(demo$demo_education)
levels(demo$demo_education) <- c("Some HS", "HS/GED", "Some College", "Associates", "BA/BS", "Postgrad", "Masters", "Phd/JD/MD")

ggplot(demo, aes(x = demo_education)) + geom_histogram(stat = "count") + theme_cowplot()

```

## Frequency and Characterization of Low and High N Groups

```{r, message = FALSE, warning= FALSE}
#Level of Neuroticism
N_level<-bsrc::bsrc.getform(protocol = panda_protocol,online = TRUE,formname = "record_registration")

#get rid of record IDs
N_level$record_id <- as.numeric(N_level$record_id)
N_level <- N_level %>% filter(!is.na(record_id))

# Low N and High N
#Low_N <- sum(N_level$panda_group == 2)
#High_N <- sum(N_level$panda_group == 1)

N_level_table <- as.data.frame(table(N_level$panda_group))
#table(N_level$panda_group)
N_level$panda_group <- as.factor(N_level$panda_group)

levels(N_level$panda_group) <- c("High", "Low")

ggplot(N_level, aes(x=as.factor(panda_group))) + geom_bar() + theme_cowplot()

```

```{r message = FALSE, warning= FALSE}

#here we can build a table of the same demographics variables as above, but split for low and high N


```

## Plotting the Distribution of N in the Sample

```{r message = FALSE, warning= FALSE}

#Score the BFAS
###set up the panda protocol environment to pull forms from
panda_protocol=list(name="PANDA",
                        redcap_uri='https://www.ctsiredcap.pitt.edu/redcap/api/',
                        token='CD9DCB5E2B863E04684C111F7A6C22F2',
                        forcenewsubinsync=TRUE)

###pull a form
bfas<-bsrc::bsrc.getform(protocol = panda_protocol,online = TRUE,formname = "bfas")

###remove unwanted variables like attention check questions
bfas_data <- select(bfas, -c(redcap_event_name, bfas_check_1, bfas_check_2))

## convert id from character variable to numeric variable
bfas_data$record_id <- as.numeric(bfas_data$record_id)
#filter out the missings we introduced by converting to numeric. This gives us all viable subjects
bfas_data <- bfas_data %>% filter(!is.na(record_id))

#just messing around: reorder the variables, then sort by bfas_39 in descending order
#xx <- bfas_data %>% select(bfas_39, bfas_8_r, bfas_18, everything()) %>% arrange(desc(bfas_39))

# create a list of the items that load on each BFAS aspect
bfas_items <- list(WIT = c("bfas_1_r", "bfas_11", "bfas_21_r", "bfas_31", "bfas_41_r", "bfas_51", "bfas_61", "bfas_71_r", "bfas_81", "bfas_91"), 
                    VOL = c("bfas_6", "bfas_16_r", "bfas_26", "bfas_36_r", "bfas_46", "bfas_56_r", "bfas_66", "bfas_76_r", "bfas_86", "bfas_96"))

#score the items
bfas_scored <- scoreItems(bfas_items, bfas_data, min = 1, max = 5)

#look at the output
print(bfas_scored)#, #short = FALSE)

#create new dataframe with the scored scales
bfas_scoredscales <- bfas_scored$scores

describe(bfas_scoredscales)

bfas_plot <- pairs.panels(bfas_scoredscales, pch = '.', lm = TRUE, cex.cor = 2)

### make it a table
bfas_scoredscales <- as.data.frame(bfas_scoredscales)

### add the subject ID
bfas_scoredscales$record_id <- bfas_data$record_id

bfas_scoredscales <- bfas_scoredscales %>% rowwise() %>% mutate(N = mean(c(WIT, VOL))) 

ggplot(bfas_scoredscales, aes(x = N)) + geom_histogram(binwidth = .25) + theme_cowplot()

#
bfas_long <- pivot_longer(bfas_scoredscales, cols = WIT:VOL, names_to = "aspect", values_to = "score")

ggplot(bfas_long, aes(x = score)) + geom_histogram(binwidth = .25) + theme_cowplot() + facet_wrap(vars(aspect))



```

## Examining BFAS Screening Scores vs. BFAS Reported Scores
```{r}

panda_screening=list(name="panda_screening",
                        redcap_uri='https://www.ctsiredcap.pitt.edu/redcap/api/',
                        token='83419F4206440B5D26B1FC3B465DB2F7',
                        forcenewsubinsync=TRUE)

screening<-bsrc::bsrc.getform(protocol = panda_screening,online = TRUE,formname = "eligibility_screening_phone_or_unit")

screening_data <- screening %>% filter(egs_whichblrub == "5")

screening_data <- screening_data %>% select(record_id, adid_1:adid_20)
```



## Test